---
title: "ggplot part 2"
author: "Amanda Mae Woodward"
date: "2024-10-22"
output: html_document
---

# Learning Outcomes
By the end of this class, students should be able to: 
- Explain how to alter information in the legend 
- Describe how to use facet wrap
- Explain how to export graphs


### Learning Outcome 1: Explain how to alter information in the legend
It can also be helpful to understand how to modify your legend: 
`+ theme(legend.position="none")` will remove the legend. You can also choose to move the legend to the top or bottom of the graph

Let's try this on a graph from the diamonds dataset: 
```{r}
library(tidyverse)
ggplot(diamonds, aes(color, price, color= cut))+ geom_point()# not super helpful 
ggplot(diamonds, aes(color, price, fill=cut)) + geom_boxplot()
```

We can also change the location: 
```{r}
ggplot(diamonds, aes(color, price, fill=cut)) + geom_boxplot()+ theme(legend.position = "bottom")
```
top, left, right, bottom, or none 

To Change the legend title, you can use a couple of different codes, depending on the type of data: 
`scale_color_manual(name="Title")` works for scatter plots filled in with a factor
`scale_fill_manual(name="Title)` should work for a bar graph filled in by a factor
`scale_color_continuous()` and `scale_fill_continuous()` should work for a numeric fill
```{r}
ggplot(diamonds, aes(color, price, fill=cut)) + geom_boxplot()+ theme(legend.position = "bottom")+ scale_fill_manual(name= "Cut of Diamond", values = c("purple", "blue", "green", "orange", "red", "yellow", ""))

```

### Practice:
```{r}
library(palmerpenguins)
data(penguins)
```

1) make a graph of bill length and bill depth. Include island as a third variable
```{r}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color=island))+ geom_point()
```

2) Move the legend to the top of the graph
```{r}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color=island))+ geom_point()+ theme(legend.position="top")

```

3) Remove the legend from the graph 
```{r}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color=island))+ geom_point()+ theme(legend.position= "none")

```

4) Change the title of the legend
```{r}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color=island))+ geom_point()+theme(legend.position="right")+ scale_color_manual(name = "Penguin Sizes by Island", values= c("purple", "blue", "lightblue"))

```

5) make a graph of bill length and bill depth. Include flipper length as a third variable
```{r}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color=flipper_length_mm))+ geom_point()
```

### Learning Outcome 2: Describe how to use facet wrap
Facet Wrap allows us to incorporate a third variable in another way. Specifically, it panels graphs so that we can make an individual graph for each level of a factor.

we need to make a graph and save it 
```{r}
ggplot(diamonds, aes(color, price, color= cut))+ geom_point()

ggplot(diamonds, aes(color, price, fill= cut))+ geom_boxplot()+ facet_wrap(~cut)

ggplot(diamonds, aes(carat,price, color= cut))+ geom_point()+geom_smooth(method="lm", color="black") + facet_wrap(~cut)
```

```{r}
ggplot(diamonds, aes(carat, price, color=cut))+ geom_point()+geom_smooth(method="lm")+facet_wrap(~color)
```

### change labels on the axes
change levels beforehand
```{r}
levels(penguins$species)<- c("Adelie Penguin", "Chinstrap Penguin", "Gentoo Penguin")

ggplot(penguins, aes(bill_length_mm, bill_depth_mm))+ geom_point()+facet_wrap(~species)
```

make a vector called labels. use `labeller=as_labeller())` in `facet_wrap()`
```{r}
speciesTitle<- c("Adelie Penguin"= "Adelie", "Chinstrap Penguin"="Chinstrap", "Gentoo Penguin"= "Gentoo") #write the current name in the dataset = name you want to present
 
ggplot(penguins, aes(bill_length_mm, bill_depth_mm))+ geom_point()+facet_wrap(~species, labeller= as_labeller(speciesTitle))
```

### Practice: 
1) create a facet wrap graph to generate a scatterplot of mpg and hp based on the number of cylinders a car has
```{r}
ggplot(mtcars, aes(hp, mpg, color=cyl))+geom_point()+facet_wrap(~cyl)
```

### Learning Outcome 3: Explain how to export graphs
to export graphs, I use the command `ggsave()`
Specifically, you can use the following arguments: 
`ggsave("name of graph", width, height, units, dpi)`
I don't usually specify a path in ggsave, but make sure my r code is in the directory I'd like it to be saved in. you can check your working directory by using this code
```{r}
getwd()#checkthat you're in your project
setwd()
```
make a graph to save
```{r}
ggplot(penguins, aes(body_mass_g, flipper_length_mm, color=species))+ geom_point()+geom_smooth(method="lm")+ scale_color_manual(name="Species of Penguin", values= c("#D7907B", "#6C4B5E", "#BBC7A4"))+ theme_classic()+ xlab("Body Mass in Grams")+ ylab("Flipper Length")+ facet_wrap(~species)+ ggtitle(label = "Graph of Body Mass vs Flipper Length")+ theme(legend.position = "bottom", element_text(size=18))
```
you can change your working directory using this code: 
```{r}
ggsave("FinalPrettyPenguinGraph.tiff", width=10, height = 8, units= "in", dpi= 300)
```
